Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-11 providence/sections/prov.tex
modified summary of providence rationale

The \Minerva stopping condition tests the tail ratios of the probability distributions (given the null and alternate hypotheses) of winner votes $K_j$ in round $j$. Note that these distributions are not conditioned on $k_{j-1}$. Thus they may be viewed as a weighted average of various distributions, each conditioned on a possible value of $K_{j-1}$. The proof of \Minerva's risk-limiting property relies on the fact that, at every stopping point, the tail of the probability distribution function given $H_0$ is at most $\alpha$ times that given $H_a$. However, because these distributions are averaged over the various values of $K_{j-1}$, this approach to the proof works only if the next round size is the same for all values of $K_{j-1}$. If not, this average pdf will not correctly represent the pdf of $K_j$. For example, if some values of $K_{j-1}$ would result in larger next round sizes, the pdf for these values of $K_{j-1}$ should not contribute to the average distribution function of $K_j$ for smaller round sizes.

For the \Providence audit we test the tail ratios of the distributions conditioned on $k_{j-1}$ and multiplied by the weighting factor. That is, we test this tail ratio separately for each weighted distribution corresponding to each possible value of $K_{j-1}$. Because of this, we no longer require that all values of $k_{j-1}$ should result in the same next round size. This results in a great deal of flexibility in multiple round audits.

>>>>

The \Minerva stopping condition tests the tail ratios of the probability distributions\footnote{given the alternate and null hypotheses respectively} of winner votes $K_j$ in round $j$. Note that these distributions are not conditioned on $k_{j-1}$. Thus each may be viewed as a weighted average of various distributions given the corresponding hypothesis, each conditioned on a possible value of $K_{j-1}$, with the weights corresponding to the probabilities of drawing that value of $K_{j-1}$.

The proof of \Minerva's risk-limiting property relies on the fact that, at every stopping point, the tail of the probability distribution function given $H_0$ is at most $\alpha$ times that given $H_a$. However, because these distributions are averaged over the various values of $K_{j-1}$, this approach to the proof works only if $n_j$ is the same for all values of $K_{j-1}$. If not, this average pdf will not correctly represent the pdf of $K_j$. For example, if some values of $K_{j-1}$ would lead to a choice of larger values of $n_j$, the pdf for these values of $K_{j-1}$ should not contribute to the average distribution function of $K_j$ for smaller values of $n_j$.

For the \Providence audit we test the tail ratios of the distributions conditioned on $k_{j-1}$ and multiplied by the weighting factor. That is, we test this tail ratio separately for each weighted distribution corresponding to each possible value of $K_{j-1}$. Because of this, we no longer require that all values of $k_{j-1}$ should result in the same values of $n_j$. This results in a great deal of flexibility in multiple round audits.
